---
title: "bullet chart and small multiples"
author: "Your name here"
date: "Date here"
---

# Details

- Who did you collaborate with: xxxxx
- Approximately how much time did you spend on this problem set: xxxxx
- What, if anything, gave you the most trouble: xxxxx


# Load, clean, and wrangle data

```{r load-packages-data, warning=FALSE, message=FALSE}
library(tidyverse)

water_usage <- read_csv("data/water_usage.csv")
unemployment <- read_csv("data/unemployment.csv")

```

# Task 1: Bullet charts

Do stuff here. first graph try to get a bullet chartby bar stacking bar.it also coordinates the sequence of fill. second graph get similar results by geom_col.

```{r}

wu<-water_usage%>%mutate(extremely_high=extremely_high-high)%>%mutate(high=high-conservative)%>%gather(key="type",value="value",conservative,high,extremely_high)

ggplot(wu)+geom_bar(aes(x=period,y=value,fill=factor(type,levels=c("extremely_high","high","conservative"))),stat="identity",stacking=TRUE)+guides(fill=guide_legend(title=""))+geom_errorbar(aes(x=period,ymax=current,ymin=current))+geom_errorbar(aes(x=period,ymax=previous,ymin=previous),color="white")

ggplot(water_usage,aes(x =period))+geom_col(aes(y = extremely_high), fill = "#f03b20") +
  geom_col(aes(y = high), fill = "darkorange") +
  geom_col(aes(y = conservative), fill = "lightskyblue") +
  geom_errorbar(aes(ymin = current, ymax = current), color = "white", width = 0.75,show.legend = TRUE) 

```



# Task 2: Small multiples

Do stuff here
```{r}
library(tidyverse)
library(ggplot2)
small<-unemployment%>%select(state,unemployment,date,region,division)%>%group_by(state)%>%filter(!any(is.na(unemployment)))%>%ungroup()
big_plot <- ggplot(small, aes(x = date, y = unemployment, color = region)) + 
  geom_line(size = 1) + 
  theme_void() +
  guides(color = guide_legend(title = NULL)) +
  theme(strip.text = element_text(face = "bold"),
        legend.position = "bottom") +
  facet_wrap(~ state, scales = "free_y")
ggsave(big_plot, filename = "giant.pdf",
       width = 20, height = 15, units = "in")
````


