---
title: "fancy plots"

---



# Hans Rosling redux

```{r load-packages-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(scales)
library(gapminder)

# Load the gapminder data from the gapminder package with data()
data(gapminder)

# Create a data frame with only rows from 1997
gapminder_1997 <- gapminder %>%
  filter(year == 1997)
```


## Univariate analysis

Plot a histogram of life expectancy in 1997 (`lifeExp`). Choose an appropriate number of bins. (You get some code to help start you off):

```{r lifeexp-hist}
ggplot(gapminder_1997, aes(x = lifeExp)) +
  geom_histogram(bins = 13)+aes(color="red")+guides(color=FALSE)
```

Plot a density plot of life expectancy in 1997. Fill it with some color so it doesn't look sad and empty.

```{r lifeexp-density}

ggplot(gapminder_1997)+geom_density(aes(x=lifeExp,color=continent))
ggplot(gapminder_1997)+geom_density(aes(x=lifeExp,fill=continent))

```

Plot a histogram of GDP per capita in 1997 (`gdpPercap`). Choose an appropriate number of bins.

```{r gdp-hist}
ggplot(gapminder_1997)+geom_histogram(aes(x=gdpPercap),bins = 30)+aes(color="red")+guides(color=FALSE)
```

Plot a density plot of GDP per capita in 1997.

```{r gdp-density}
ggplot(gapminder_1997)+geom_density(aes(x=gdpPercap))

```

## Univariate analysis by groups

Plot multiple violin plots of GDP per capita in 1997 by continent. Fill the continents with different colors. Add points at 50% transparency. (You get some code to help start you off):

```{r gdp-continent}
ggplot(gapminder_1997, aes(x = continent, y = gdpPercap)) +
  geom_violin()+aes(fill=continent,alpha=0.5)+guides(alpha=FALSE)
```

Plot multiple boxplots of GDP per capita in 1997 by continent. Fill the continents with different colors.

```{r gdp-continent-box}
ggplot(gapminder_1997, aes(x = continent, y = gdpPercap)) +
  geom_boxplot()+aes(fill=continent,alpha=0.5)+guides(alpha=FALSE)
```

Plot multiple violin plots of life expectancy in 1997 by continent, also with filled continents and semi-transparent points (hint: do basically what you did above, but with `lifeExp` instead of `gdpPercap`)

```{r lifeexp-continent}
ggplot(gapminder_1997, aes(x = continent, y = lifeExp)) +
  geom_violin()+aes(fill=continent,alpha=0.5)+guides(alpha=FALSE)
```

Plot overlapping density plots of life expectancy in 1997 across continents. Oceania has very few observations, so omit it from the data (I create a filtered data frame for you below). Fill each continent with a color and make each density plot 50% transparent.

```{r continent-densities}
gapminder_1997_sans_oceania <- gapminder_1997 %>%
  filter(continent != "Oceania")

ggplot(gapminder_1997_sans_oceania, aes(x=lifeExp))+geom_density(aes(fill=continent))+aes(alpha=0.5)+guides(alpha=FALSE)
```

## Bivariate analysis

Plot health (`lifeExp`) vs. wealth (`gdpPercap`) in 1997. Color each point by continent. (You get some code to help start you off):

```{r health-wealth-basic}
ggplot(gapminder_1997, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(aes(color=continent,alpha=0.5,size=3))+guides(alpha=FALSE,size=FALSE)
```

Make that same plot, but add `coord_trans(x = "log10")` as a layer.

```{r health-wealth-transformed}
ggplot(gapminder_1997, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(aes(color=continent,alpha=0.5,size=3))+guides(alpha=FALSE,size=FALSE)+coord_trans(x = "log10")
```

What's different?

Plot health vs. wealth again (without a logged x-axis), and add a `geom_smooth()` layer.

```{r health-wealth-smooth}

ggplot(gapminder_1997, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(aes(color=continent,alpha=0.5,size=3))+guides(alpha=FALSE,size=FALSE)+geom_smooth()
```

By default, R will choose `method = "loess"` to plot the line. What is "loess"? (hint: see pages 240-41 in Cairo). Change the smoothing method to `method = "lm"` (`lm` here stands for "linear model")

```{r health-wealth-lm}
ggplot(gapminder_1997, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(aes(color=continent,alpha=0.5,size=3))+guides(alpha=FALSE,size=FALSE)+geom_smooth(method="lm")
```

What's different?

Plot health vs. wealth *with* a logged x-axis *and* with a loess smooth.

```{r health-wealth-log-loess}
ggplot(gapminder_1997, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(aes(color=continent,alpha=0.5,size=3))+guides(alpha=FALSE,size=FALSE)+coord_trans(x="log10")+geom_smooth()
```

Plot health vs. wealth *with* a logged x-axis *and* a linear smooth (`lm`). 

```{r health-wealth-log-lm}
ggplot(gapminder_1997, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(aes(color=continent,alpha=0.5,size=3))+guides(alpha=FALSE,size=FALSE)+coord_trans(x="log10")+geom_smooth(method="lm")
```


## Fancy stuff

Here's a fancy, production-quality version of the health-wealth plot. Explain what each of these layers are doing:

- `ggplot(gapminder_1997, aes(...))`: 
- `geom_point()`: 
- `guides()`: 
- `labs()`: 
- `scale_x_continuous()`: 
- `scale_size_continuous()`: 
- `scale_color_viridis_d()`:
- `coord_trans()`: 
- `theme_light()`: 
- `theme()`: (what are each of the options doing in `theme()`?)
- `ggsave()`

```{r health-wealth-fancy}
library(viridis)
nice_health_wealth <- ggplot(gapminder_1997, aes(x = gdpPercap, y = lifeExp, 
                                                 size = pop, color = continent)) +
  geom_point() + 
  guides(size = FALSE, color = guide_legend(title = NULL)) +
  labs(x = "GDP per capita", y = "Life expectancy",
       title = "Global health and wealth",
       subtitle = "142 countries in 1997",
       caption = "Source: The Gapminder Project") +
  scale_x_continuous(labels = dollar) +
  scale_size_continuous(range = c(1, 10)) +
  scale_color_viridis(option = "inferno", begin = 0.2, end = 0.9,discrete = TRUE) +
  coord_trans(x = "log10") + 
  theme_light() + 
  theme(legend.position = "bottom",
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(face = "bold", size = rel(1.5)),
        plot.subtitle = element_text(color = "grey60"),
        plot.caption = element_text(color = "grey60"))
nice_health_wealth

ggsave(nice_health_wealth, filename = "nice_health_wealth.pdf",
       width = 7, height = 5, units = "in")
ggsave(nice_health_wealth, filename = "nice_health_wealth.png",
       width = 7, height = 5, units = "in")
```


## Multiple years

Look at the relationship between health and wealth in 1992, 1997, 2002, and 2007 all in one plot. To do this, you can't use the `gapminder_1997` data frame anymore, since that's just 1997. You'll need to create a new data frame. 

Color each point by continent and resize each point by population. Place each of the four years in a separate facet (hint: look at the documentation for `facet_wrap()`). (You get some code to help start you off):

```{r health-wealth-post-1992}
gapminder_after_1992 <- gapminder %>% filter(year >= 1992)

ggplot(gapminder_after_1992, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(aes(color=continent,size=pop)) + 
  guides(size = FALSE, color = guide_legend(title = NULL)) +
  labs(x = "GDP per capita", y = "Life expectancy",
       title = "Global health and wealth",
       subtitle = "142 countries in every 5 years",
       caption = "Source: The Gapminder Project") +
  scale_x_continuous(labels = dollar) +
  scale_size_continuous(range = c(1, 10)) +
  scale_color_viridis(option="D",begin=0.2,end=0.9,discrete=TRUE)+
  coord_trans(x = "log10")+facet_wrap(~year)
```

Create a similar plot to show the relationship between health and wealth in 1952, 1957, 1962, and 1967. Again, you won't be able to use either the `gapminder_1997` or the `gapminder_after_1992` data frames. You'll have to create a new data frame. And I won't give you code for that.

```{r health-wealth-early-cold-war}
hwb<-gapminder%>%filter(year>=1952,year<=1967)
ggplot(hwb,aes(x = gdpPercap, y = lifeExp))+geom_point(aes(color=continent,size=pop,alpha=0.5)) + 
  guides(size = FALSE, color = guide_legend(title = NULL),alpha=FALSE) +
  labs(x = "GDP per capita", y = "Life expectancy",
       title = "Global health and wealth",
       subtitle = "142 countries in every 5 years",
       caption = "Source: The Gapminder Project") +
  scale_x_continuous(labels = dollar) +
  scale_size_continuous(range = c(1, 10)) +
  scale_color_viridis(option="C",begin=0.2,end=0.9,discrete=TRUE)+
  coord_trans(x = "log10")+facet_wrap(~year)
```

## Bonus fun times: ridge plots

Using your newfound visualization skills (and referencing [the `ggridges` vignette](https://cran.r-project.org/web/packages/ggridges/vignettes/introduction.html)), make a ridge plot showing the distribution of either life expectancy or GDP per capita over time (or over each of the continents). Save this plot as both a PDF and a PNG in your output folder with `ggsave()`

(You don't have to do this, but it'd be a great learning experience if you did)

```{r gapminder-ridgeplot}
library(ggridges)

```


## Extra bonus fun times: interactivity

For even more fun, try making an interactive HTML plot. The easiest way to do this is to use the `plotly` package (install it with the "Packages" panel in RStudio), and then to use its `ggplotly()` function.

I've given you some commented-out code below (commented out so that R doesn't yell at you about the code not working when you knit). 

Also, check out [the documentation](https://plot.ly/ggplot2/), especially [this page](https://plot.ly/ggplot2/interactive-tooltip/) about customizing the tooltips that show up when you hover over points or areas.

(Again, you definitely don't have to do this, but this kind of interactivity is fun, relatively easy, and super impressive for future employers)

```{r interactive, message=FALSE}
# library(plotly)
# 
# my_cool_plot <- ggplot(...)
#
# my_cool_plot
# 
# ggplotly(my_cool_plot)
```
